Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I

### 2024-01-18 theart.qmd
bib

Participants were assessed with both MMSE (Stepankova et al., 2014; [@folstein1975] and MoCA [@kopecek2016]; [@nasreddine2005] to measure overall cognitive performance. Moreover, a comprehensive neuropsychological assessment was performed in accordance with MDS Task Force Level 2 criteria for MCI in PD [@litvan2012]. We described our battery including a regression based calculator for normative scores in another study [@bezdicek2017]. Besides other neuropsychological tests, the comprehensive assessment employed Clock Drawing Test (CDT) and Letter Fluency. To establish cognitive performance in individual cognitive domains according to Level 1 criteria for PDD, we used test scores proposed by Dubois et al., [@dubois2007] and their analogues in MoCA, see Table A for details.

@@

To measure independence in activities of daily living, we administered Functional Activities Questionnaire (FAQ; Bezdicek et al., 201; [@pfeffer1982]. To assess neuropsychiatric functioning, we used Beck Depression Inventory II (BDI-II; [@ciharova2020]; [@beck1996] and State-Trait Anxiety Inventory (STAI; Spielberg et al., 1970, Mullner et al., 1980). Psychotic symptoms were assessed in an interview by a trained psychiatrist.

>>>>

Participants were assessed with both MMSE [@stepankova2014; @folstein1975] and MoCA [@kopecek2016]; [@nasreddine2005] to measure overall cognitive performance. Moreover, a comprehensive neuropsychological assessment was performed in accordance with MDS Task Force Level 2 criteria for MCI in PD [@litvan2012]. We described our battery including a regression based calculator for normative scores in another study [@bezdicek2017]. Besides other neuropsychological tests, the comprehensive assessment employed Clock Drawing Test (CDT) and Letter Fluency. To establish cognitive performance in individual cognitive domains according to Level 1 criteria for PDD, we used test scores proposed by [@dubois2007] and their analogues in MoCA, see Table A for details.

@@

To measure independence in activities of daily living, we administered Functional Activities Questionnaire (FAQ; [@bezdicek2011; @pfeffer1982]. To assess neuropsychiatric functioning, we used Beck Depression Inventory II (BDI-II; [@ciharova2020]; [@beck1996] and State-Trait Anxiety Inventory (STAI; Spielberg et al., 1970, @mullner1980\]. Psychotic symptoms were assessed in an interview by a trained psychiatrist.
